---
pagetitle: "CAMPSIS"
date: ""
author: ""
output: github_document
---

<!-- badges: start -->
[![R-CMD-check](https://github.com/Calvagone/campsis/workflows/R-CMD-check/badge.svg)](https://github.com/Calvagone/campsis/actions)
<!-- badges: end -->

## Requirements

* R package `campsismod` must be installed beforehand
* Simulation engine must be installed too (either `RxODE` or `mrgsolve`)

## Installation
Install the latest stable release with the authentication token you have received:
  
```{r, eval=FALSE}
devtools::install_github("Calvagone/campsis", ref="main", auth_token="AUTH_TOKEN", force=TRUE)
```

## Basic example

```{r, results='hide', echo=F, message=F, warning=F}
library(campsis)
```

Create your dataset:

```{r}
ds <- Dataset(50)
ds <- ds %>% add(Bolus(time=0, amount=1000))
ds <- ds %>% add(Bolus(time=24, amount=2000))
ds <- ds %>% add(Observations(times=seq(0, 48, by=0.5)))
```

Load your own model or use a built-in model from the library:

```{r}
model <- model_library$advan4_trans4
```

Simulate your results with your preferred simulation engine:

```{r}
results <- model %>% simulate(dataset=ds, dest="RxODE", seed=1)
```

Plot your results:

```{r get_started_shaded_plot, fig.align='center', fig.height=4, fig.width=8}
shadedPlot(results, "CP")
```