---
pagetitle: "pmxsim"
date: ""
author: ""
output: github_document
---

# pmxsim
A generic clinical trial simulation platform.

## Requirements

* R package `pmxmod` must be installed beforehand
* Simulation engine must be installed too (either `RxODE` or `mrgsolve`)

## Installation
Install the current development version:
  
```{r, eval=FALSE}
remotes::install_github("Calvagone/pmxsim@dev")
```

## Some examples

### Simulate boluses

First import the `pmxmod` and `pmxsim` packages:

```{r, message=FALSE}
library(pmxmod)
library(pmxsim)
```

Load 2-compartment PK model from built-in model library:

```{r}
model <- getNONMEMModelTemplate(advan=4, trans=4)
```

Create your dataset using `pmxsim`. For instance, let's give 1000mg QD for 3 days and observe every hour.

```{r}
dataset <- Dataset()
dataset <- dataset %>% add(Bolus(time=0, amount=1000))
dataset <- dataset %>% add(Bolus(time=24, amount=1000))
dataset <- dataset %>% add(Bolus(time=48, amount=1000))
dataset <- dataset %>% add(Observations(times=seq(0,72, by=1)))
```

See all methods that can be applied on a dataset:

```{r}
methods(class=class(dataset))
showMethods("add", classes=class(dataset))
```


Simulate this very simple protocol:

```{r}
results <- model %>% simulate(dataset, dest="RxODE", seed=1)
head(results)
```

Plot these results:

```{r}
spaguettiPlot(results, "CP")
```

Simulate more subjects:

```{r}
dataset <- Dataset(subjects=100)
dataset <- dataset %>% add(Bolus(time=0, amount=1000))
dataset <- dataset %>% add(Bolus(time=24, amount=1000))
dataset <- dataset %>% add(Bolus(time=48, amount=1000))
dataset <- dataset %>% add(Observations(times=seq(0,72, by=1)))
results <- model %>% simulate(dataset, dest="RxODE", seed=1)
spaguettiPlot(results, "CP")
```

A shaded plot may also be used:

```{r}
shadedPlot(results, "CP")
```

We could also simulate two different treatment arms. Say the first arm receives 1000mg QD and the second arm 2000mg QD.

```{r}
arm1 <- Arm(id=1, subjects=50)
arm2 <- Arm(id=2, subjects=50)

arm1 <- arm1 %>% add(Bolus(time=0, amount=1000))
arm1 <- arm1 %>% add(Bolus(time=24, amount=1000))
arm1 <- arm1 %>% add(Bolus(time=48, amount=1000))
arm1 <- arm1 %>% add(Observations(times=seq(0,72, by=1)))

arm2 <- arm2 %>% add(Bolus(time=0, amount=2000))
arm2 <- arm2 %>% add(Bolus(time=24, amount=2000))
arm2 <- arm2 %>% add(Bolus(time=48, amount=2000))
arm2 <- arm2 %>% add(Observations(times=seq(0,72, by=1)))

dataset <- Dataset() %>% add(arm1) %>% add(arm2)

results <- model %>% simulate(dataset, dest="RxODE", seed=1)
shadedPlot(results, "CP", scenarios="ARM")
```

### Simulate infusions

Load 2-compartment PK model without absorption from built-in model library:

```{r}
model <- getNONMEMModelTemplate(advan=3, trans=4)
```

1000mg is infused in central compartment in 5 hours of time.

```{r}
dataset <- Dataset(10)
dataset <- dataset %>% add(Infusion(time=0, amount=1000, compartment=1))
dataset <- dataset %>% add(Observations(times=seq(0,24, by=0.5)))

# 5 hours duration
dataset <- dataset %>% add(TreatmentInfusionDuration(compartment=1, distribution=ConstantDistribution(5)))

results <- model %>% simulate(dataset, dest="RxODE", seed=1)
spaguettiPlot(results, "CP")
```

Let's add some variability on the infusion duration:

```{r}
dataset <- Dataset(10)
dataset <- dataset %>% add(Infusion(time=0, amount=1000, compartment=1))
dataset <- dataset %>% add(Observations(times=seq(0,24, by=0.5)))

# 5 hours duration, with 20% CV
dataset <- dataset %>% add(TreatmentInfusionDuration(compartment=1, distribution=LogNormalDistribution(meanlog=log(5), sdlog=0.2)))

results <- model %>% simulate(dataset, dest="RxODE", seed=1)
spaguettiPlot(results, "CP")
```