---
title: "Uncertainty levels"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Uncertainty levels}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, results='hide', echo=F, message=F, warning=F}
library(pmxmod)
library(pmxsim)
```

### Simulate with all uncertainties

Let's use a simple 1-compartment model with absorption compartment to illustrate the different levels of uncertainties.

```{r}
getModel <- function() {
  model_library$advan2_trans2
}
model <- getModel()
model
```

We're going to use a very basic dataset. 1000 mg QD shall be administered for a week.

```{r}
getDataset <- function() {
  ds <- Dataset(25)
  for (day in 0:6) {
    ds <- ds %>% add(Bolus(time=day*24, amount=1000))
  }
  ds <- ds %>% add(Observations(times=seq(0,24*7,by=4)))
}
```

All subjects are different due to IIV and RUV.

```{r uncertainties_all_enabled , fig.align='center', fig.height=4, fig.width=8}
results <- model %>% simulate(dataset=getDataset(), dest="RxODE", seed=1)
spaguettiPlot(results, "Y")
```

### Simulate without RUV

Disabling RUV is done as follows:

```{r}
model <- getModel() %>% disable(c("RUV"))
model@parameters
```

In that case, Y (the observed concentration) is identical as CP (the model-simulated plasma concentration).

```{r uncertainties_no_ruv_y , fig.align='center', fig.height=4, fig.width=8}
results <- model %>% simulate(dataset=getDataset(), dest="RxODE", seed=1)
spaguettiPlot(results, "Y")
```

```{r uncertainties_no_ruv_cp , fig.align='center', fig.height=4, fig.width=8}
spaguettiPlot(results, "CP")
```

### Simulate without RUV and IIV

Disabling RUV and IIV is done as follows:

```{r}
model <- getModel() %>% disable(c("IIV", "RUV"))
model@parameters
```

Now, the typical profile is shown for all subjects.

```{r uncertainties_no_ruv_no_iiv , fig.align='center', fig.height=4, fig.width=8}
results <- model %>% simulate(dataset=getDataset(), dest="RxODE", seed=1)
spaguettiPlot(results, "Y")
```