---
title: "Bioavailability"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Bioavailability}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, results='hide', echo=F, message=F, warning=F}
library(pmxmod)
library(pmxsim)
```

There are 2 ways to implement bioavailability in `pmxsim`:

* in the model: bioavailability is defined for each compartment
* in the dataset: bioavailability is defined for each bolus or infusion

In the first case, the simulation engine will take care of the bioavailability.
In the second case, `pmxsim` will adapt automatically the amount injected through the dataset (AMT column).

### Bioavailability implement in model

Let's use a 2-compartment model with absorption compartment to illustrate how this can be achieved.

```{r}
model <- model_library$advan4_trans4
```

For this example, we're going to define a bioavailability `F1` for this absorption compartment.

First let's create a new parameter `F1`, log-normally distributed with a median of 0.75 and 20% CV.

```{r}
model <- model %>% add(Theta(name="F1", index=6, value=0.75))
model <- model %>% add(Omega(name="F1", index=6, index2=6, value=20, type="cv%"))
```

Now, let's add an equation to the drug model to define `F1`.
```{r}
model <- model %>% addEquation("F1", rhs="THETA_F1*exp(ETA_F1)")
```

Finally, we need to tell `pmxsim` that `F1` corresponds to a bioavailability.

```{r}
model <- model %>% add(Bioavailability(compartment=1, rhs="F1"))
```

Our persisted drug model would look like this:

```{r}
model
```

Now, let's now give a simple bolus and simulate with and without `F1`.

```{r}
ds1 <- Dataset(50)
ds1 <- ds1 %>% add(Bolus(time=0, amount=1000))
ds1 <- ds1 %>% add(Observations(times=seq(0,24,by=0.5)))
```


```{r bioavailability_model , fig.align='center', fig.height=4, fig.width=8}
results_f1 <- model %>% simulate(dataset=ds1, dest="RxODE", seed=1)
results_no_f1 <- model_library$advan4_trans4 %>% simulate(dataset=ds1, dest="RxODE", seed=1)
gridExtra::grid.arrange(shadedPlot(results_f1, "CP"), shadedPlot(results_no_f1, "CP"), nrow=1)
```

### Bioavailability inplemented in dataset

The same simulation can be performed by adapting the column `AMT` in the dataset.
Let's redefine the dataset.

We need to sample `F1` values. This can be done as follows:

```{r}
distribution <- ParameterDistribution(model=model, theta="F1", omega="F1")
f1Values <- (distribution %>% sample(as.integer(50)))@sampled_values
f1Values
```

Then, we can inject them into the dataset and simulate.

```{r}
ds2 <- Dataset(50)
ds2 <- ds2 %>% add(Bolus(time=0, amount=1000, f=f1Values))
ds2 <- ds2 %>% add(Observations(times=seq(0,24,by=0.5)))
```

```{r bioavailability_dataset , fig.align='center', fig.height=4, fig.width=8}
results_f1 <- model_library$advan4_trans4 %>% simulate(dataset=ds2, dest="RxODE", seed=1)
shadedPlot(results_f1, "CP")
```

The result is identical.