---
title: "Inter-occasion variability"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Inter-occasion variability}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, results='hide', echo=F, message=F, warning=F}
library(campsis)
```

This vignette shows how inter-occasion variability can be added on a parameter at each administration.

### Treatment IOV on KA

Let's use a 2-compartment model with absorption compartment for this example.

```{r}
model <- model_library$advan4_trans4
```

We're going to add a term `IOV_KA` on `KA`. This can be done as follows:

```{r}
model <- model %>% replace(Equation("KA", "THETA_KA*exp(ETA_KA + IOV_KA)"))
```

This model will not run unless we give some values for `IOV_KA`. This can achieved by adding `IOV` to the dataset.
The following function will create a simple dataset with or without `IOV` on demand.

```{r}
getDataset <- function(iov=FALSE) {
  ds <- Dataset(50)
  ds <- ds %>% add(Bolus(time=0, amount=1000, compartment=1))
  ds <- ds %>% add(Bolus(time=24, amount=1000, compartment=1))
  ds <- ds %>% add(Bolus(time=48, amount=1000, compartment=1))
  ds <- ds %>% add(Observations(times=seq(0,72, by=0.5)))
  if (iov) {
    # Add 100% CV to KA
    ds <- ds %>% add(IOV(colname="IOV_KA", distribution=NormalDistribution(mean=0, sd=1)))
  } else {
    # Add zero IOV or covariate
    ds <- ds %>% add(IOV(colname="IOV_KA", distribution=0))
  }
  return(ds)
}
```

We can now run the model with `IOV` on `KA` and without.

```{r lag_time_model , fig.align='center', fig.height=4, fig.width=8}
results_iov <- model %>% simulate(dataset=getDataset(TRUE), dest="RxODE", seed=1)
results_no_iov <- model %>% simulate(dataset=getDataset(FALSE), dest="RxODE", seed=1)
gridExtra::grid.arrange(shadedPlot(results_iov, "CP"), shadedPlot(results_no_iov, "CP"), nrow=1)
```
