---
title: "Initial conditions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Initial conditions}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, results='hide', echo=F, message=F, warning=F}
library(pmxmod)
library(pmxsim)
```

This vignette shows how initial conditions may be used in `pmxsim`.

### Init central compartment

Assume the following 2-compartment model is used.

```{r}
model <- model_library$advan3_trans4
```

We'd like to init the central compartment to a predefined value, e.g. 1000.  
This can be achieved as follows.

```{r}
model <- model %>% add(InitialCondition(compartment=1, rhs="1000"))
```

The resulting model has now a new block `[INIT]` which describes the initial condition:

```{r}
model
```

Let's now create a dataset with observations-only.

```{r}
getDataset <- function() {
  ds <- Dataset(50)
  ds <- ds %>% add(Observations(times=seq(0,72, by=0.5)))
  return(ds)
}
```

We can now simulate this model:

```{r initial_condition , fig.align='center', fig.height=4, fig.width=8}
results <- model %>% simulate(dataset=getDataset(), dest="RxODE", seed=1)
shadedPlot(results, "CP")
```
