---
title: "Replicate your study"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Replicate your study}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, results='hide', echo=F, message=F, warning=F}
library(campsis)
```

This vignette shows how a simulation can be replicated.

### Simulate uncertainty on percentiles

Assume the following model is used. This model is a 2-compartment model without absorption compartment which has been fitted on some data.

```{r}
model <- model_library$my_model1
```

It contains a variance-covariance matrix with the uncertainty on all the estimated parameters.

```{r}
model
```

We are interested to see the uncertainty on the simulated concentration percentiles over time.
Let's mimic the protocol that was implemented in the study.

```{r}
ds <- Dataset(50)
for (day in 0:6) {
  ds <- ds %>% add(Infusion(time=day*24, amount=1000, compartment=1))
}
ds <- ds %>% add(Observations(times=seq(0, 7*24)))
```

Let's now simulate this model with parameter uncertainty.  
Argument `replicates` specifies how many times the simulation is replicated.  
Argument `outfun` is a function that is going to be called after each simulation on the output data frame.

```{r}
results <- model %>% simulate(dataset=ds, dest="RxODE", replicates=10, outfun=~PI(.x, output="Y"), seed=1)
results %>% head()
```

Function `vpcPlot` allows to quickly visualize such results.

```{r replicate_your_study_varcov , fig.align='center', fig.height=4, fig.width=8}
vpcPlot(results)
```

