---
title: "Complex PK/PD models from litterature"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Complex PK/PD models from litterature}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, results='hide', echo=F, message=F, warning=F}
library(campsis)
```

This vignette intends to demonstrate that CAMPSIS can be used to implement almost any PK/PD model, including complex ones.

### Filgrastim PK/PD model

Load the filgrastim PK/PD model from the model library as follows. Please note that this model was translated from NONMEM code. The original model file can be found [here](http://repository.ddmore.eu/model/DDMODEL00000077) on the DDMORE repository.

```{r}
library(campsis)
pkpd <- model_library$filgrastim_pkpd_model
pkpd
```

Let's create a fictive cohort of 25 subjects receiving filgrastim 10 μg/kg for a week following subcutaneous administration.

```{r}
dataset <- Dataset(25) %>% 
  add(Bolus(time=0, amount=10, compartment=1, ii=24, addl=6)) %>% 
  add(Infusion(time=0, amount=10, compartment=2, ii=24, addl=6)) %>%
  add(Observations(times=0:168)) %>%
  add(Covariate("ROUT", 0)) %>%
  add(Covariate("BAS", 0.02)) %>%
  add(Covariate("WT", UniformDistribution(60,80))) %>%
  add(DoseAdaptation("WT*AMT"))
```

A quick simulation gives us the plasma concentration of filgrastim, as well as the absolute neutrophil count (ANC):

```{r filgrastim_pkpd_model, fig.align='center', fig.height=7, fig.width=8}
results <- pkpd %>% simulate(dataset=dataset, seed=1)

p1 <- spaghettiPlot(results, "ZCP") + ggplot2::ylab("G-CSF Serum Concentration (ng/mL)")
p2 <- spaghettiPlot(results, "ZNB") + ggplot2::ylab("ANC (10^3 cells/μL)")

gridExtra::grid.arrange(p1, p2, ncol=1)
```
