---
title: "Complex PK/PD models from litterature"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Complex PK/PD models from litterature}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, results='hide', echo=F, message=F, warning=F}
library(campsis)
```

This vignette intends to demonstrate that CAMPSIS can be used to implement almost any PK/PD model, including complex ones.

### Filgrastim PK/PD model

Load the filgrastim PK/PD model from the model library as follows. Please note that this model was translated from NONMEM code. The original model file can be found [here](http://repository.ddmore.eu/model/DDMODEL00000077) on the DDMORE repository.

```{r}
pkpd <- model_library$filgrastim_pkpd_model
pkpd
```

Let's create a fictive cohort of 25 subjects receiving filgrastim 10 μg/kg for a week following subcutaneous administration.

```{r}
dataset <- Dataset(25) %>% 
  add(Bolus(time=0, amount=10, compartment=1, ii=24, addl=6)) %>% 
  add(Infusion(time=0, amount=10, compartment=2, ii=24, addl=6)) %>%
  add(Observations(times=0:168)) %>%
  add(Covariate("ROUT", 0)) %>%
  add(Covariate("BAS", 0.02)) %>%
  add(Covariate("WT", UniformDistribution(60,80))) %>%
  add(DoseAdaptation("WT*AMT"))
```

A quick simulation gives us the plasma concentration of filgrastim, as well as the absolute neutrophil count (ANC):

```{r filgrastim_pkpd_model, fig.align='center', fig.height=7, fig.width=8}
results <- pkpd %>% simulate(dataset=dataset, seed=1)

p1 <- spaghettiPlot(results, "ZCP") + ggplot2::ylab("G-CSF Serum Concentration (ng/mL)")
p2 <- spaghettiPlot(results, "ZNB") + ggplot2::ylab("ANC (10^3 cells/μL)")

gridExtra::grid.arrange(p1, p2, ncol=1)
```

### Target mediated drug disposition Model of CPHPC

Load the target mediated drug disposition Model of CPHPC from the model library as follows. Please note that this model was translated from NONMEM code. The original model file can be found [here](http://repository.ddmore.foundation/model/DDMODEL00000262) on the DDMORE repository.

```{r}
pkpd <- model_library$cphpc_pkpd_model
pkpd
```

Let's create 3 fictive cohorts of 25 subjects each, all receiving a 1-hour infusion of 10 mg CPHPC.

```{r}
arm <- Arm(subjects=25) %>% 
  add(Infusion(time=0, amount=10, duration=1)) %>%
  add(Observations(times=seq(0.1,24,by=0.1)))

arm1 <- arm %>% add(Covariate("CRCL", UniformDistribution(80,120))) %>% setLabel("Normal renal function")
arm2 <- arm %>% add(Covariate("CRCL", UniformDistribution(50,80))) %>% setLabel("Mild renal impairment")
arm3 <- arm %>% add(Covariate("CRCL", UniformDistribution(30,50))) %>% setLabel("Moderate renal impairment")
dataset <- Dataset() %>% add(c(arm1, arm2, arm3)) 
```

A quick simulation gives us the concentration of CPHPC over 24 hours, as well as the concentration in serum amyloid P (SAP), for each cohort:

```{r cphpc_sas_pkpd_model, fig.align='center', fig.height=7, fig.width=8}
results <- pkpd %>% simulate(dataset=dataset, seed=1)

# Reorder ARM labels
results <- results %>% dplyr::mutate(ARM=factor(ARM, levels=c("Normal renal function", "Mild renal impairment", "Moderate renal impairment")))

# Unit conversion
results <- results %>% dplyr::mutate(C1=C1*340.37*1e6, C3=C3*5*25000*1e3)
  
p1 <- spaghettiPlot(results, "C1", "ARM") + ggplot2::ylab("CPHPC (ng/mL)") + ggplot2::scale_y_log10() + ggplot2::facet_wrap(~ARM)
p2 <- spaghettiPlot(results, "C3", "ARM") + ggplot2::ylab("SAP (mg/L)") + ggplot2::scale_y_log10() + ggplot2::facet_wrap(~ARM)

gridExtra::grid.arrange(p1, p2, ncol=1)
```