---
title: "Run your simulation in parallel"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Run your simulation in parallel}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, results='hide', echo=F, message=F, warning=F}
library(campsis)
library(tictoc)
library(ggplot2)
library(dplyr)
```

This vignette explains how Campsis can benefit from several CPU cores for running your simulation efficiently.

### Base model and dataset

```{r, echo=FALSE, eval=F}
# GitHub  : use Dataset(100)
# Vignette: use Dataset(1000)
```

```{r}
model <- model_suite$pk$`2cpt_fo_mm`

dataset <- Dataset(100) %>%
  add(Bolus(time=0, amount=100, ii=12, addl=10)) %>%
  add(Observations(times=0:(11*12)))
```

### Run replicates in parallel

```{r, echo=FALSE, eval=F}
# GitHub  : use replicates=10
# Vignette: use replicates=100
```

Sequential run:

```{r, message=F}
tic()
results <- simulate(model=model, dataset=dataset, dest="mrgsolve", seed=1, outfun=~PI(.x, output="CONC"), replicates=10)
toc()
```

Using 6 cores:

```{r}
settings <- Settings(Hardware(cpu=6, replicate_parallel=TRUE))
```

```{r, message=F}
tic()
results <- simulate(model=model, dataset=dataset, dest="mrgsolve", seed=1, outfun=~PI(.x, output="CONC"), replicates=10, settings=settings)
toc()
```

```{r replicates_in_parallel, fig.align='center', fig.height=4, fig.width=8}
vpcPlot(results)
```

Since there is no uncertainty on the parameters and since 1000 patients are simulated in each replicate, the confidence intervals on the percentiles are very low.

### Run scenarios in parallel

Instead of giving a fixed dose, let's make the dose dynamic using a `DOSE` covariate:

```{r}
dataset_ <- dataset %>%
  add(Covariate("DOSE", 0)) %>%
  add(DoseAdaptation("AMT*DOSE"))
```

Let's create one scenario per dose to be tested:

```{r}
scenarios <- Scenarios()
for (dose in c(0.5,1,5,10,50,100,500,1000,5000,10000,50000,100000)) {
  scenarios <- scenarios %>%
    add(Scenario(name=paste0("DOSE=", dose), dataset=dataset_ %>% replace(Covariate("DOSE", dose))))
}
```

Sequential run:

```{r, message=F}
tic()
results <- simulate(model=model, dataset=dataset_, dest="mrgsolve", seed=1, scenarios=scenarios)
toc()
```

Using 6 cores (plan is auto-setup):

```{r}
settings <- Settings(Hardware(cpu=6, scenario_parallel=TRUE))
```

```{r, message=F}
tic()
results <- simulate(model=model, dataset=dataset_, dest="mrgsolve", seed=1, scenarios=scenarios, settings=settings)
toc()
```

Using 6 cores (plan already setup from last execution):

```{r}
settings <- Settings(Hardware(cpu=6, scenario_parallel=TRUE, auto_setup_plan=FALSE))
```

```{r, message=F}
tic()
results <- simulate(model=model, dataset=dataset_, dest="mrgsolve", seed=1, scenarios=scenarios, settings=settings)
toc()
```

Plot results:

```{r scenarios_in_parallel, fig.align='center', fig.height=4, fig.width=8}
# Re-arrange scenarios by natural order
results <- results %>% mutate(SCENARIO=factor(SCENARIO, levels=unique(SCENARIO)))

shadedPlot(results, "CONC", "SCENARIO") +
  facet_wrap(~SCENARIO, ncol=4, scales="free_y") +
  guides(colour="none", fill="none")
```

### Export dataset in parallel

In some particular cases, when the number of subjects is important and/or the dataset is complex, it may be interesting to export the dataset in parallel.
Let's illustrate this feature using a dataset that contains a lot of subjects and treatment IOV (which is costly).

```{r, echo=FALSE, eval=F}
# GitHub  : use setSubjects(4000)
# Vignette: use setSubjects(24000)
```

```{r}
dataset_ <- dataset %>%
  setSubjects(4000) %>%
  add(IOV("IOV_KA", distribution=NormalDistribution(mean=0, sd=0.1))) # This step is costly
```

```{r}
model_ <- model %>%
  replaceAll("ETA_KA", "ETA_KA + IOV_KA")

```

Sequential run:

```{r, message=F}
tic()
settings <- Settings(Hardware(slice_size=4000))
results <- simulate(model=model_, dataset=dataset_, dest="mrgsolve", seed=1, settings=settings)
toc()
```

Using 6 cores (plan is auto-setup):

```{r}
settings <- Settings(Hardware(cpu=6, dataset_parallel=TRUE, dataset_slice_size=4000, slice_size=4000))
```

```{r, message=F}
tic()
results <- simulate(model=model_, dataset=dataset_, dest="mrgsolve", seed=1, settings=settings)
toc()
```

Using 6 cores (plan already setup from last execution):

```{r}
settings <- Settings(Hardware(cpu=6, dataset_parallel=TRUE, dataset_slice_size=4000, slice_size=4000, auto_setup_plan=FALSE))
```

```{r, message=F}
tic()
results <- simulate(model=model_, dataset=dataset_, dest="mrgsolve", seed=1, settings=settings)
toc()
```

Plot results:

```{r dataset_in_parallel, fig.align='center', fig.height=4, fig.width=8}
shadedPlot(results, "CONC")
```

### Run slices in parallel

```{r, echo=FALSE, eval=F}
# GitHub  : use Dataset(10)
# Vignette: use Dataset(200)
```

It may be useful to simulate slices in parallel when the simulation time per individual is high (e.g. long simulation).
To illustrate this topic, let's dose and observe a drug over a 6-month period.

```{r}
dataset_ <- Dataset(10) %>%
  add(Bolus(time=0, amount=100, ii=12, addl=364)) %>%
  add(Observations(times=0:(365*12)))
```

Sequential run (`rxode2`) :

```{r, message=F}
tic()
results <- simulate(model=model, dataset=dataset_, dest="rxode2", seed=1)
toc()
```

Sequential run (`mrgsolve`) :

```{r, message=F}
tic()
results <- simulate(model=model, dataset=dataset_, dest="mrgsolve", seed=1)
toc()
```

Using 6 cores (`rxode2`, plan is auto-setup):

```{r}
settings <- Settings(Hardware(cpu=6, slice_parallel=TRUE))
```

```{r, message=F}
tic()
results <- simulate(model=model, dataset=dataset_, dest="rxode2", seed=1, settings=settings)
toc()
```

Using 6 cores (`mrgsolve`, plan is auto-setup):

```{r}
settings <- Settings(Hardware(cpu=6, slice_parallel=TRUE))
```

```{r, message=F}
tic()
results <- simulate(model=model, dataset=dataset_, dest="mrgsolve", seed=1, settings=settings)
toc()
```

Please note that the default slice size for `mrgsolve` is 500, which means that only 1 core was used in the previous example.
For `rxode2`, which works with a much smaller slice size of 6 subjects, paralleling slices may be interesting for long simulations, as demonstrated here.

