---
title: "Progress bar"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Progress bar}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, results='hide', echo=F, message=F, warning=F}
library(campsis)
```

This vignette explains how you can track the simulation progress thanks to the package `progressr`.

### Track the simulation progress in an R script

Load package `progressr` as follows:

```{r, warning=FALSE}
library(progressr)
```

The easiest way to track the progress is to add the following snippet once for all in your script. By doing so, any call to the simulate method of `campsis` will display the progress bar.

```{r, echo=TRUE, eval=FALSE}
handlers(global=TRUE)
```

By default, the progress bar will only give the progress as a percentage. Any user-custom handler may be provided. Please have a look at the official [documentation](https://cran.r-project.org/web/packages/progressr/vignettes/progressr-intro.html) (section 'Customizing how progress is reported').

If you want to use the default handler from `campsis`, which gives you more details about what's being simulated and what's the remaining time (ETA), you can write:
```{r, echo=TRUE, eval=FALSE}
handlers(campsis_handler())
```

If you don't want your handler(s) to be global, you can also explicitly call the method `with_progress`. The snippet below is an example of simulation where this method is called.

```{r, with_progress_example, fig.align='center', fig.height=4, fig.width=8}
dataset <- Dataset(1000) %>%
  add(Infusion(time=0, amount=1000, compartment=1, ii=24, addl=6)) %>%
  add(Observations(seq(0, 7*24)))

model <- model_suite$pk$`1cpt_zo_abs_lag`
results <- with_progress(simulate(model=model, dataset=dataset, dest="mrgsolve", seed=1, replicates=3))
shadedPlot(results, "CONC", "replicate")
```

Any handler may be provided as well:

```{r}
results <- with_progress(simulate(model=model, dataset=dataset, dest="mrgsolve", seed=1, replicates=3), handlers=campsis_handler())
```

### Track the simulation progress in a targets project

The [targets](https://books.ropensci.org/targets/) package is a Make-like pipeline tool for Statistics and data science in R. With targets, you can maintain a reproducible workflow without repeating yourself. It is the ideal pipeline tool to use for medium to large simulation projects with Campsis.

The following script (`_targets.R`) gives you a brief overview of what you can achieve with targets and how the progress bar can be enabled.
It is important to mention that `handlers(global=TRUE)` can't be used in such a script. If you try to do so, an error message will pop up.

```{r, echo=TRUE, eval=FALSE}
library(targets)

source("R/my_script.R")

# Packages loaded by targets
packages <- c("campsis", "progressr")
tar_option_set(packages=packages)

# Enable progress bar
options(progressr.enable=TRUE)
progressr::handlers(campsis::campsis_handler())

list(
  tar_target(
    model,
    model_suite$pk$`1cpt_zo_abs_lag`
  ),
  tar_target(
    dataset,
    makeDataset(subjects=1000, dose=1000)
  ),
  tar_target(
    results,
    runSimulation(model=model, dataset=dataset, replicates=3)
  )
)
```

The R folder contains as much as possible of the code (or logic) being executed, in the form of R functions. The snippet below shows the content of `my_script.R`.
An explicit call to `with_progress` will make the progress bar appear when executing the target `results`.

```{r, echo=TRUE, eval=FALSE}
makeDataset <- function(subjects, dose) {
  dataset <- Dataset(subjects=subjects) %>%
    add(Infusion(time=0, amount=dose, compartment=1, ii=24, addl=6)) %>%
    add(Observations(seq(0, 7*24)))
  return(dataset)
}

runSimulation <- function(model, dataset, replicates) {
  results <- with_progress(simulate(model=model, dataset=dataset, dest="mrgsolve",
                                    seed=1, replicates=replicates))
  return(results)
}
```

This small project can be downloaded by clicking the link below.
```{r echo=FALSE}
xfun::embed_dir('resources/Targets Squeletton/', text="Download targets squeletton")
```
